---
title: "The rosareg package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The rosareg package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rosareg)
```

# Introduction

This package contains functions I find useful for MATH5773 Regression Analysis at OU. The results of these functions are used repeatedly in the course, and are vital for valid regression analyses.

The `myLAreg()` function produces a named list with the following: model summary, n (number of observations), k (number of beta parameters), beta estimates, RSS, s-squared, s, the Design & Response Matrices, and the data frame.

The `myFnest()` function produces a list containing the nested F-statistic, the F_alpha value, and result of the hypothesis test. This is also known as the "Hierarchical F-Test".

Finally, the function, `myMSdata()`, is more of a shortcut for calling in the data sets we utilize in the course. NOTE: this only works on my computer :) 

We will now look at examples of each function using the `PRODQUAL` data set.

```{r}
prod <- myMSdata("PRODQUAL")
```

# Example `myLAreg()`

```{r}
ylm <- lm(QUALITY ~ TEMP + PRESSURE + TEMP:PRESSURE + I(TEMP^2) + I(PRESSURE^2), data = prod)

myLAreg(ylm)
```

# Example `myFnest()`

```{r}
zlm <- lm(QUALITY ~ TEMP + PRESSURE + TEMP:PRESSURE, data = prod)

myFnest(objc = ylm, objr = zlm, alpha = 0.05)
```






